Building Large-Scale Bilingual Knowledge Base from Multi-Encyclopedia

### 2015-05-18 nlpcc/paper.tex
doc

\subsection{Definitions}

>>>>

\subsection{Definitions}
Here we list definitions involved in the later sections/
Definition 1: A Encyclopedia is considered as a collection of articles, category system and links, which can be defined as a 3-tuple:
\begin{equation}
W = <A,C,L>
\end{equation} 
where A denotes articles, C denotes categories, and L denotes links in W.
We involve four encyclopedias, which are expressed as Wen, Wzh, Whd and Wbb.
Definition 2: According to Section \ref {sec:}
